Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-26 Arxiv/main.tex
rewrite differential privacy proof case 1

\noindent \textbf{Differential Privacy.} 
\begin{definition}
$\epsilon-$differential privacy.

@@

\begin{definition}
$(\epsilon,\delta)-$differential privacy.

@@

In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_convert} and \ref{lem_cadinality}.

\begin{lem}
\label{lem_score_pro_convert}
  Given $\hexpmech(\dataobs)$ and $r', r'' \in \candidateset{\dataobs}$, then following holds:
  $$
  \ux{r'} = \ux{r''} \iff \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  $$  
\end{lem}
\begin{proof} of lemma \ref{lem_score_pro_convert}.
\begin{itemize}
  \item $\implies$
  \begin{equation*}
  \begin{split}
  \ux{r'} = \ux{r''} 
  & \implies \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r''] \\
  & \implies \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  \end{split}
  \end{equation*}

@@

    \begin{equation*}
  \begin{split}
  & \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''} \\
  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r'']\\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & \implies  \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & \implies \ux{r'} = \ux{r''}.
  \end{split}
  \end{equation*}
\end{itemize}

@@

  Define $\cardinality{r}$ as the cardinality of $R_r$ s.t. $ R_r = \{ r' : \ux{r'} = \ux{r}, r' \in \candidateset{\dataobs}\} \subset \candidateset{\dataobs}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$, 
\end{definition}

\begin{lem}
\label{lem_cadinality}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_cadinality}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_convert} in $R_r$, \\
$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, let $\epsilon\geq 0$ and $\ux{r} + k >=0$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

@@

Let $\ux{t} = \ux{r} + k$.
In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
\begin{itemize}
  \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
  \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
\end{itemize}

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$ and $k \geq 0$.\\
  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$.\\
  By Lemma \ref{lem_score_pro_convert}, $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r} \hexpmechPr{\dataobs}{z = r}$.\\
  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$.\\
  $\implies$\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}

  \item $u(\dataobs, r) \neq 0$, $\ux{r} + k \neq 0$ and $-\ux{r} < k < 0$

  \item $\ux{r} = 0$.\\
  By $\ux{r} = 0$, $\cardinality{r} = 1$.\\
  Destruct $k$:
  \begin{itemize}
    \item $k = 0$:\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
    & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}
    \item $k \neq 0$:\\
    By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$.\\
    $\implies$\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
    & < 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}

  \end{itemize}
  \item $\ux{r} \neq 0, \ux{r} + k = 0$
    By $\ux{r} + k = 0$, $\cardinality{t} = 1$.\\
    By $\ux{r} \neq 0$, $\cardinality{r} = 2$.\\
    $\implies$\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 1 \cdot \hexpmechPr{\dataobs}{z = t}\\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & = e^{\ln 2} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & = e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}

>>>>

\noindent \textbf{Differential Privacy.} 
\begin{definition}
\label{def_epsilon_dp}
$\epsilon-$differential privacy.

@@

\begin{definition}
\label{def_epsilon_delta_dp}
$(\epsilon,\delta)-$differential privacy.

@@

In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.

\begin{lem}
\label{lem_score_pro_eq}
  Given $\hexpmech(\dataobs)$ and $r', r'' \in \candidateset{\dataobs}$, then following holds:
  $$
  \ux{r'} = \ux{r''} \iff \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  $$  
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_eq}.
\begin{itemize}
  \item $\implies$
  \begin{equation*}
  \begin{split}
  & \ux{r'} = \ux{r''} \\
  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
  & \implies \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & Apply\ Definition\ \ref{def_smoo} :\\
  & \implies \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  \end{split}
  \end{equation*}

@@

    \begin{equation*}
  \begin{split}
  & \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''} \\
  & Apply\ Definition\ \ref{def_smoo} :\\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & \implies  \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
  & \implies \ux{r'} = \ux{r''}.
  \end{split}
  \end{equation*}
\end{itemize}

@@

  Define $\cardinality{r}$ as the cardinality of $R_r$ s.t. $ R_r = \{ r' | r' \in \candidateset{\dataobs}\ s.t. \ \ux{r'} = \ux{r}, \}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$, 
\end{definition}

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, let $\epsilon\geq 0$ and $\ux{r} + k >=0$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

@@

In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
\begin{itemize}
  \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
  \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
\end{itemize}

\todo{
In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
\begin{itemize}
  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 1\}$.
  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 2\}$.
\end{itemize}
}

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{r} = 2$}\\
  Destruct k:
  \begin{itemize}
    \item  $k \geq 0$: $\implies$\\
      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

    \item $-\ux{r} < k < 0$: $\implies$\\

      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \cardinality{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

  \item $\ux{r} = 0, \ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
        By $\ux{r} = 0$, $\cardinality{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
        By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
        $\implies$\\
        \begin{equation*}
        \begin{split}
        LHS 
        & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
        & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ Definition\ \ref{def_smoo})\\
        & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{r} = 1) \\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{t} = 2)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

  \item $\ux{r} \neq 0, \ux{r} + k = 0$ \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}\\
      By $\ux{r} + k = 0$, $\cardinality{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
      By $\ux{r} \neq 0$, $\cardinality{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
      $\implies$\\
      \begin{equation*}
      \begin{split}
      LHS   
      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{t} = 1)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

  \item $\ux{r} = 0, \ux{r} + k = 0$: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}\\
